Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-29 paper/lagrangeSpontaneousSimilarity2017.tex
more comments on writing

The time scattering transform is computed over a range frame sizes, from 25 ms to 1 second. The Q factor is set to 8 in order to obtain a frequency decomposition that is equivalent to the mel scale \vl{The mel scale has a varying quality factor, so I don't see how this can be right}. As the frame size increase, the dimensionality increases. Unless otherwise stated, the frame size is one second. The resulting scattering features are then logarithmically compressed and normalized using the median computed over the whole dataset.

@@

>>>>

The time scattering transform is computed over a range frame sizes, from 25 ms to 1 second. The Q factor is set to 8 in order to obtain a frequency decomposition that is equivalent to the mel scale. As the frame size increase, the dimensionality increases. Unless otherwise stated, the frame size is one second. The resulting scattering features are then logarithmically compressed and normalized using the median computed over the whole dataset.

\vl{The mel scale has a varying quality factor, so I don't see how this can be right.}
\vl{I understand what "logarithmically compressed" and "normalized using the median" because I worked on this before but,
for someone who is less experienced, this might not be precise enough.}

@@

\vl{The paragraph above is very peremptory and at the same time quite vague.
I could quote many tasks in which there is no need to "target in some way" the scattering transform to obtain better results than MFCC.
What scientific conclusion are we drawing here? @writing}
